Sparse Word Embeddings for Multi-domain Machine Translation

### 2019-05-01 2019/emnlp/sparse.tex
work on the introduction

\title{Sparse Word Embedding for Multi-domain Machine Translation}

@@

>>>>

\title{Sparse Word Embeddings for Multi-domain Machine Translation}

@@

\section{Introduction \label{sec:introduction}}
% The problem
Owing to the development of flexible and powerful architectures based on neural networks \cite{bahdanau2014neural;Vaswani17attention}, Machine Translation (MT) has made significant progress over the past years, and constitute the standard for most production engines to-date. One issue which repeatedly pops up with neural MT is the need to perform training with large parallel corpus, typically consisting of millions of parallel sentences as close as possible to the application domain. A lot of the recent research effort has focused on building MT systems in low data conditions for instance building multi-lingual \cite{} MTs or even building systems without any data \cite{}.

Another important scenario for industrial MT systems is to adapt an neural system trained using a parallel data in one  domain to the peculiarity of other domains. Domain Adaption (DA) in MT is an ancient issue \cite{Foster07amixture,Axelrod11domain}, which comes in various guise, and for which a number of solutions has been studied \cite{Chu18asurvey}. The typical setting is \emph{supervised adaptation}, where a (small) amount of data of the target domain of interest is used to fine-tuned the parameters of a system trained on a large amount of texts in a source domain. We study here a different scenario, multi-domain adaptation \cite{Farajian17multidomain}, where we would like to use heterogenous data sources to train a unique system that would work well for all domains.

Multi-domain adaptation is conceptually close to multi-lingual MT\cite{}, or more generally to multi-task learning \cite{}, and can be approached in a number of ways.
